---
title: "Q10 of Ra-Rh dominate sites analysis"
author: "Jinshi"
date: "4/18/2019"
output: html_document
---


```{r preliminaries, message=FALSE, include=FALSE, echo=FALSE}
# Set chunks defaults; these options will be applied to all subsequent chunks
knitr::opts_chunk$set(results = 'hide', message = TRUE, include = TRUE, echo = FALSE,
                      fig.height = 4.5, fig.width = 8)

# Constants
OUTPUT_DIR		<- "outputs/"
LOG_DIR			<- "logs/"
SEPARATOR		<- "-------------------------------------------"

DATA_DIR <- 'data'


# Create output and log folders if they do not exist
if(!file.exists(OUTPUT_DIR)) dir.create(OUTPUT_DIR)
if(!file.exists(LOG_DIR)) dir.create( LOG_DIR )

# install.packages('cowplot')
# Load required packages
library(cowplot)
library(data.table)
library(dplyr)
library(ggplot2)
theme_set(theme_bw())
library(lubridate)
library(kableExtra)
library(cowplot)
library(knitr)
library("ggpubr")
library(reshape)
library(ggplot2)
# install.packages("ggmap")
library(ggmap)
# install.packages("maps")
library(maps)
# install.packages("mapdata")
library(mapdata)

library(tidyr)

# Source all needed functions
source('functions.R')
```



```{r}
# input data
srdb_v4 <- read.csv(paste0(DATA_DIR,'/', 'srdbv4.csv'), header = T) # SRDB_V4 data
MGRsD <- read.csv(paste0(DATA_DIR,'/', "MGRsDAllData.csv"), header=T) # MGRsD data
DGRhRa <- read.csv(paste0(DATA_DIR,'/', "DGRhRaD.csv"), header = T) #Daily time scale global Rh, Ra, and Q10 of Rh, Ra dataset

HGRsD <- read.csv(paste0(DATA_DIR,'/', "HGRsD_OriginalData.csv"), header = T) # Global hourly time scale Rs data
HGRsD$DN <- ifelse (is.na(HGRsD$TimeLable), 'NotA', ifelse(HGRsD$TimeLable >=7 & HGRsD$TimeLable <= 18, 'Day', 'Night') )
# sort(unique(DGRhRa$StudyNumber))
```



```{r, fig.height=6, fig.width=8}
# test Q10 under Ra and Rh dominant sites
plot_grid(
    Q10_test(srdb_v4, 'Q10_0_10', expression(A~(0-10~degree~C) )),
    Q10_test(srdb_v4, 'Q10_5_15', expression(B~(5-15~degree~C) )),
    Q10_test(srdb_v4, 'Q10_10_20', expression(C~(10-20~degree~C) )),
    Q10_test(srdb_v4, 'Q10_0_20', expression(D~(0-20~degree~C) )),
ncol = 2)  

```


```{r}
srdb_sub <- rbind(filtration (srdb_v4, 'Q10_0_10', 'RC_annual'),
                  filtration (srdb_v4, 'Q10_5_15', 'RC_annual'),
                  filtration (srdb_v4, 'Q10_10_20', 'RC_annual'),
                  filtration (srdb_v4, 'Q10_0_20', 'RC_annual')
                  )
```


```{r}
ggplot(aes(RC_annual, Q10, col = Q10_type), data = srdb_sub) + geom_point( shape = 1) +
  geom_smooth( aes(RC_annual, Q10), method = 'lm', se = FALSE ) + 
  ylim (0, 7.5) 
# why change order and name of legend not work here?
  # scale_fill_discrete(name='Q10 group', breaks = c('Q10_0_10', 'Q10_5_15', 'Q10_10_20', 'Q10_0_20')
  #                     , labels = c('Q10_0_10', 'Q10_5_15', 'Q10_10_20', 'Q10_0_20')
  #                     )
```


```{r}
srdb_sub <- rbind(Q10_RC_drought (srdb_v4, 'Q10_0_10', 'SPI', 'RC_annual'),
                  Q10_RC_drought (srdb_v4, 'Q10_0_10', 'pdsi', 'RC_annual')
                  )

# srdb_sub <- srdb_sub[!is.na(srdb_sub$Ra_Rh_dom), ]

ggplot(aes(Drought, Q10, col = Ecosystem_type), data = srdb_sub ) + geom_point(alpha = 0.25) + geom_smooth(method = "lm" ) +
  facet_grid(Drought_label ~ Leaf_habit)
```

```{r}
srdb_sub <- rbind(Q10_RC_drought (srdb_v4, 'Q10_5_15', 'SPI', 'RC_annual'),
                  Q10_RC_drought (srdb_v4, 'Q10_5_15', 'pdsi', 'RC_annual')
                  )

ggplot(aes(Drought, Q10, col = Ecosystem_type), data = srdb_sub ) + geom_point(alpha = 0.25) + geom_smooth(method = "lm" ) +
  facet_grid(Drought_label ~ Leaf_habit)

```

```{r}
srdb_sub <- rbind(Q10_RC_drought (srdb_v4, 'Q10_10_20', 'SPI', 'RC_annual'),
                  Q10_RC_drought (srdb_v4, 'Q10_10_20', 'pdsi', 'RC_annual')
                  )

ggplot(aes(Drought, Q10, col = Ecosystem_type), data = srdb_sub ) + geom_point(alpha = 0.25) + geom_smooth(method = "lm" ) +
  facet_grid(Drought_label ~ Leaf_habit)

```

---
title: "rcq10"
author: "BBL"
date: "4/22/2019"
output: html_document
---

```{r setup, include=FALSE}
srdb_v4 %>% 
  as_tibble() %>% 
  select(RC_annual, Biome, Leaf_habit, starts_with("Q10")) -> 
  srdb_v4
srdb_v4 %>% 
  select(RC_annual, Biome, Leaf_habit, Q10_0_10, Q10_5_15, Q10_0_20, Q10_10_20) %>% 
  gather(Label, Q10, starts_with("Q10")) ->
  srdb_v4_standard
srdb_v4 %>% 
  select(RC_annual, Biome, Leaf_habit, Q10 = Q10_other1, Q10_other1_temp_min, Q10_other1_temp_max) %>% 
  mutate(Label = paste("Q10", Q10_other1_temp_min, Q10_other1_temp_max, sep = "_")) %>% 
  select(-Q10_other1_temp_min, -Q10_other1_temp_max) ->
  srdb_v4_custom1
srdb_v4 %>% 
  select(RC_annual, Biome, Leaf_habit, Q10 = Q10_other2, Q10_other2_temp_min, Q10_other2_temp_max) %>% 
  mutate(Label = paste("Q10", Q10_other2_temp_min, Q10_other2_temp_max, sep = "_")) %>% 
  select(-Q10_other2_temp_min, -Q10_other2_temp_max) ->
  srdb_v4_custom2
bind_rows(srdb_v4_standard, srdb_v4_custom1, srdb_v4_custom2) %>% 
  filter(!is.na(RC_annual), !is.na(Q10)) %>% 
  separate(Label, sep = "_", into = c("X", "temp_low", "temp_high"), convert = TRUE) %>% 
  mutate(Temp_avg = (temp_low + temp_high) / 2,
        RC_group = cut(RC_annual, c(-0.1, 0.5, 1.0), labels = c("Heterotrophic", "Autotrophic")),
        Leaf_habit = factor(Leaf_habit, levels = c("Deciduous", "Mixed", "Evergreen"))) ->
  srdb_v4_q10
```

Still just playing around.


```{r plot2}
srdb_v4_q10 %>% 
  group_by(RC_group) %>% 
  summarise(Q10 = median(Q10)) -> 
  lbls
ggplot(srdb_v4_q10, aes(x = Q10, color = RC_group)) + 
  geom_density(size = 1) + 
  ggtitle(paste("N =", nrow(srdb_v4_q10))) + 
  geom_vline(data=lbls, aes(xintercept = Q10, color = RC_group), linetype = 2)
ggplot(srdb_v4_q10, aes(RC_annual, Q10, color = Leaf_habit)) + 
  geom_point() + 
  geom_smooth(method = "lm") +
  ggtitle(paste("N =", nrow(srdb_v4_q10)))
ggplot(srdb_v4_q10, aes(Temp_avg, Q10)) + 
  geom_point() + 
  geom_smooth(method = "lm") +
  facet_wrap(~Leaf_habit)
```

And

```{r}
srdb_v4_q10 %>% 
  filter(RC_annual > 0) %>% 
  group_by(Leaf_habit, RC_group) %>% 
  summarise(Q10 = paste(round(median(Q10), 2), "N =", n())) %>% 
  spread(RC_group, Q10) %>% 
  kableExtra::kable()
```

Treating RC as a continuous variable:

```{r}
m1 <- lm(Q10 ~ Leaf_habit * Temp_avg * RC_annual, data = srdb_v4_q10)
#car::Anova(m1, type = "III")
m1_red <- MASS::stepAIC(m1, direction = "both", trace = 0)
car::Anova(m1_red, type = "III")
summary(m1_red)
```

Treating RC as a group (heterotrophic and autotrohic):

```{r}
m2 <- lm(Q10 ~ Leaf_habit * Temp_avg * RC_group, data = srdb_v4_q10)
#car::Anova(m2, type = "III")
m2_red <- MASS::stepAIC(m2, direction = "both", trace = 0)
car::Anova(m2_red, type = "III")
summary(m2_red)
```









* Test using data from MGRsD

```{r}
# plot sites distribution of MGRsD
worldMap <- map_data(map="world")
siteInfor <- summarySE (data=MGRsD, measurevar='Rs_Norm', groupvars=c("Latitude","Longitude"))
siteInfor <- siteInfor[, c(1:3)]
siteInfor <- siteInfor[which(!is.na(siteInfor$Latitude)),]
siteInfor$N <- siteInfor$N*0.25

sitemap <- ggplot(data = worldMap) + 
  geom_polygon(aes(x = long, y = lat , fill = region , group = group, alpha = 0.1), color = "white") + 
  coord_fixed(1.3) +
  theme(axis.text.y   = element_text(size=12),
        axis.text.x   = element_text(size=12),
        
        axis.title.y   = element_text(size=13, margin = margin(t = 0, r = 12, b = 0, l = 0)),
        axis.title.x   = element_text(size=13, margin = margin(t = 12, r = 0, b = 0, l = 0)),
        
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        panel.border = element_rect(colour = "black", fill=NA, size=1.25))+
  theme(legend.position="none")+
  scale_x_continuous(name="Longitude", breaks=seq(-180,180, 30),labels = seq(-180,180, 30))+
  scale_y_continuous(name="Latitude", limits = c(-60,90),breaks=seq(-90,90,15),labels = seq(-90,90,15))+
  
  geom_point(data = siteInfor, aes(x=siteInfor$Longitude, y=siteInfor$Latitude), color = "blue"
             , size = mean(siteInfor$N)*0.1 + siteInfor$N*0.05, alpha = 7/10) + 
  guides(fill=FALSE)  # do this to leave off the color legend

print(sitemap)
```

```{r}
MGRsD_Rh <- nls(Rh_Norm ~ (R) * exp(Q * Tsoil) 
                    , data = DGRhRa, start = list(R = 1.4, Q = 0.035), trace = TRUE)

summary(MGRsD_Rh)
exp(0.041294*(10)) 

# MGRsD-Ra_root
MGRsD_Ra <- nls(Ra_Norm ~ (R) * exp(Q * Tsoil) 
                    , data = DGRhRa, start = list(R = 1.4, Q = 0.035), trace = TRUE)

summary(MGRsD_Ra)
exp(0.064298*10)
```



```{r}
# Tsoil and Tm_Del vs. Rh and Ra comparison
# colnames(DGRhRa)
RhRa_TDel <- function (sdata) {
  sub_Rh <- subset(sdata, !is.na(Rh_Norm), select = c(StudyNumber, Rh_Norm, Tm_Del ))
  sub_Rh$Source <- "DGRsD_TDel"
  sub_Rh$Rs_comp <- "Rh"
  colnames(sub_Rh) <- c("StudyNumber", "Rs", "Tm", "Source", "Rs_comp")

  sub_Ra <- subset(sdata, !is.na(Ra_Norm), select = c(StudyNumber, Ra_Norm, Tm_Del))
  sub_Ra$Source <- "DGRsD_TDel"
  sub_Ra$Rs_comp <- "Ra"
  colnames(sub_Ra) <- c("StudyNumber", "Rs", "Tm", "Source", "Rs_comp")
  
  sub_Rh_Ra <- rbind(sub_Rh, sub_Ra)
  return(sub_Rh_Ra)
}

# 
RhRa_Tsoil <- function (sdata) {
  sub_Rh <- subset(sdata, !is.na(Rh_Norm), select = c(StudyNumber, Rh_Norm, Tsoil ))
  sub_Rh$Source <- "DGRsD_Tsoil"
  sub_Rh$Rs_comp <- "Rh"
  colnames(sub_Rh) <- c("StudyNumber", "Rs", "Tm", "Source", "Rs_comp")
  
  sub_Ra <- subset(sdata, !is.na(Ra_Norm), select = c(StudyNumber, Ra_Norm, Tsoil))
  sub_Ra$Source <- "DGRsD_Tsoil"
  sub_Ra$Rs_comp <- "Ra"
  colnames(sub_Ra) <- c("StudyNumber", "Rs", "Tm", "Source", "Rs_comp")
  
  sub_Rh_Ra <- rbind(sub_Rh, sub_Ra)
  return(sub_Rh_Ra)
}

RhRa_T <- rbind(RhRa_TDel(DGRhRa), RhRa_Tsoil(DGRhRa)) 

Q10_plot <- ggplot(aes(Tm, Rs), data = RhRa_MD) + geom_point(col=alpha("black", 0.25)) + 
  facet_grid(Source ~ Rs_comp)
print(Q10_plot)

```




```{r}
qplot(Tm_Del, Tsoil, data = subset(DGRhRa, DGRhRa$Tm_Del > (-25)))
# subset(DGRhRa, DGRhRa$Tsoil>0 & DGRhRa$Tm_Del< (-25), select = c(StudyNumber, Tsoil, Tm_Del)) #1304 November
summary(lm(Tsoil~Tm_Del, data = subset(DGRhRa, DGRhRa$Tm_Del > (-25)) ))

subset(DGRhRa, is.na(DGRhRa$Tsoil)) %>% nrow() # 696 NA Tsoil
```




```{r}
# subset(DGRhRa, DGRhRa$Tsoil>0 & DGRhRa$Tm_Del< (-25), select = c(StudyNumber, Tsoil, Tm_Del)) #1304 November
nrow(subset(MGRsD, is.na(MGRsD$TS))) # 3239 NA Tsoil
nrow(subset(MGRsD, MGRsD$Latitude < 0)) # 974 North hetmosphere data
subset(MGRsD, is.na(IGBP_FromPaper)) %>% nrow()
MGRsD[MGRsD$TS>30 & MGRsD$Tm < 0 & !is.na(MGRsD$TS),]$TS <- MGRsD[MGRsD$TS>30 & MGRsD$Tm < 0 & !is.na(MGRsD$TS),]$Tm
qplot(Tm, TS, data = MGRsD)
summary(lm(TS~Tm, data = MGRsD ))
```



```{r, include=FALSE}
Q10_Rs_Ra_Rh <- Q10_cal(DGRhRa)
```



```{r}
# compare calculated mean Q10 of Rs, Rh, and Ra with reported from paper
nrow(Q10_Rs_Ra_Rh)
min(Q10_Rs_Ra_Rh$obs)

max(Q10_Rs_Ra_Rh$Q10_Rs_Paper, na.rm = TRUE)
min(Q10_Rs_Ra_Rh$Q10_Rs_Paper, na.rm = TRUE)

max(Q10_Rs_Ra_Rh$Q10_Rh_Paper, na.rm = TRUE)
min(Q10_Rs_Ra_Rh$Q10_Rh_Paper, na.rm = TRUE)

max(Q10_Rs_Ra_Rh$Q10_Ra_Paper, na.rm = TRUE)
min(Q10_Rs_Ra_Rh$Q10_Ra_Paper, na.rm = TRUE)

mean(Q10_Rs_Ra_Rh$Q10_Rs, na.rm = TRUE)
mean(Q10_Rs_Ra_Rh$Q10_Rs_Paper, na.rm = TRUE)

mean(Q10_Rs_Ra_Rh$Q10_Rh, na.rm = TRUE)
mean(Q10_Rs_Ra_Rh$Q10_Rh_Paper, na.rm = TRUE)

mean(Q10_Rs_Ra_Rh[Q10_Rs_Ra_Rh$Q10_Ra < 20,]$Q10_Ra, na.rm = TRUE)
mean(Q10_Rs_Ra_Rh$Q10_Ra_Paper, na.rm = TRUE)
```


```{r}
qplot(data = Q10_Rs_Ra_Rh, p_Q, geom = 'histogram')
qplot(data = Q10_Rs_Ra_Rh, p_Q_Rh, geom = 'histogram')
qplot(data = Q10_Rs_Ra_Rh, p_Q_Ra, geom = 'histogram')

qplot(data = Q10_Rs_Ra_Rh, Q10_Rs, geom = 'histogram')
qplot(data = Q10_Rs_Ra_Rh, Q10_Rh, geom = 'histogram')
qplot(data = Q10_Rs_Ra_Rh, Q10_Ra, geom = 'histogram')
```





```{r, fig.width=12, fig.height=4}
# Some studies' calculated Q10 > 10, check by study
check_outler(DGRhRa, 177)
check_outler(DGRhRa, 1304)
check_outler(DGRhRa, 3561)
check_outler(DGRhRa, 3921)
check_outler(DGRhRa, 4062)
check_outler(DGRhRa, 4159)
check_outler(DGRhRa, 4166)
```


```{r, fig.width=12, fig.height=4}
# Compare reported Q10 vs. calculated Q10 
plot_grid(qplot(Q10_Rs, Q10_Rs_Paper, data = Q10_Rs_Ra_Rh) + geom_abline(slope = 1, intercept = 0) + geom_smooth(method = "lm") + xlim (0,10)
    ,qplot(Q10_Rh, Q10_Rh_Paper, data = Q10_Rs_Ra_Rh) + geom_abline(slope = 1, intercept = 0) + geom_smooth(method = "lm") + xlim (0,10)
    ,qplot(Q10_Ra, Q10_Ra_Paper, data = subset(Q10_Rs_Ra_Rh, Q10_Rs_Ra_Rh$Q10_Ra < 20)) + xlim (0,10) + 
        geom_abline(slope = 1, intercept = 0) + geom_smooth(method = "lm")
    , ncol = 3
    )

```


```{r}
# summary of Rs, Rh, and Ra observations from DGRhRa dataset
nrow(Q10_Rs_Ra_Rh) # 252 sites
length(unique(Q10_Rs_Ra_Rh$var_Study.i.)) # 149 papers

nrow( subset(Q10_Rs_Ra_Rh, !is.na(Q10_Rs_Ra_Rh$Q10_Rs)))
nrow( subset(Q10_Rs_Ra_Rh, !is.na(Q10_Rs_Ra_Rh$Q10_Rs_Paper)))

nrow( subset(Q10_Rs_Ra_Rh, !is.na(Q10_Rs_Ra_Rh$Q10_Rh)) )
nrow( subset(Q10_Rs_Ra_Rh, !is.na(Q10_Rs_Ra_Rh$Q10_Rh_Paper)) )

nrow( subset(Q10_Rs_Ra_Rh, !is.na(Q10_Rs_Ra_Rh$Q10_Ra)) )
nrow( subset(Q10_Rs_Ra_Rh, !is.na(Q10_Rs_Ra_Rh$Q10_Ra_Paper)) )

```

* Q10 of Ra larger than Q10 of Rh, both reported Q10 and calculated Q10 resulted similar results
```{r, fig.height=9, fig.width=8}
Q10_comparison (Q10_Rs_Ra_Rh)
```

* Q10 show no significant difference among partition method (need further statistic test)
* 'Bare soil' method tend to has lower [(heterotrophic respiration)/(total respiration ratio)] (HC) 
* ‘Trench' tend to has higher HC
```{r, fig.height=9, fig.width=9}
# Plot Q10 
RhRa_partition (Q10_Rs_Ra_Rh, DGRhRa)
```

* Q10 show no significant difference among Biome groups
* Bare sparsed vegetation (BSV) has higher HC
* Tundra has lower HC

```{r, fig.height=9, fig.width=9}
# Plot Q10 
RhRa_biome (Q10_Rs_Ra_Rh, DGRhRa)
```


* HC dynamic within 12 months shows that grassland and savanna tend to have higher HC in winter (but not significant? need future statistic test)

```{r, fig.height=12, fig.width=6}
RhRa_month(DGRhRa)
```

* Rs in spring and winter is more sensitive to temperature change than in summer and fall in almost all Biomes
```{r, fig.height=6, fig.width=12}
# how to add slope information and Q10 in each panel
Q10_Season_Biome(MGRsD)
```

* Rs is more sensitive to temperature change in nighttime than in daytime
```{r}
# Using HGRsD test day and night time Q10
HGRsD_DayNight_test (HGRsD)
```

```{r, include=FALSE}
Q10_DN_site <- Q10_DayNight_byStudy (HGRsD)
```

```{r}
Q10_DN_Comp(Q10_DN_site)
```

```{r, fig.width=3, fig.height=8}
Q10_DN_Biome(Q10_DN_site)
```



